---
title: "Alcohol vs Seat choice"
author: "Tyler Frasier"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction


$H_0$ There isnt a difference between the alcohol consumption and the row you sit in.

$H_A$ There is a difference based on the alcohol you consume and the row you sit in. 

# Methods

The response variable is numerical and the explanatory variable is catagorical. Therefore we use numerical~cat.

## Results 


## Graphical Results 
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```


The row in the back seats consumes a lot more drink than the front and middle row. The front and middle seems to drink about the same.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
So the back row by the 3rd quarter drank 3x more alcohol a week than the front row and 2x more thhan the middle.


## Inferential Tests


```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


The p value is 0.000116 is less than 0.005. This means that you rejected the null which is thhere is no difference and i concluded that there is a difference based on the alcohol consumed by row.

```{r}
plot(TukeyHSD(model1))
```


We dont have evidence that the difference in the alcohol consumption between the middle and front row. The only difference we got is from the back row consuming more than the front and middle row. 

## Conclusions
Is there a difference between the alcohol consumed between the row you choose to sit in??
There is a difference in consumption of alcohol based on which row you sit in because by the graph it shows that the guys in the back drink more than the front and middle combined. The p value is less than the average which is 0.005.So that means you reject the null.

