---
title: "Alcohol vs Seat choice"
author: "Tyler Frasier"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction


$H_0$ There isnt a difference between the alcohol consumption and the row you sit in.

$H_A$ There is a difference based on the alcohol you consume and the row you sit in. 

# Methods

The response variable is numerical and the explanatory variable is catagorical. Therefore we use numerical~cat.

## Results 


## Graphical Results 
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```


The row in the back seats consumes a lot more drink than the front and middle row. The front and middle seems to drink about the same.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
So the back row by the 3rd quarter drank 3x more alcohol a week than the front row and 2x more thhan the middle.



## Inferential Tests


## Conclusions


